# Calculate the potencial exponent for the scaled contribution for different places

We add a new column to each dataset with the normaliced order (between 0 and 1) named "orderScaled" (I know its a bad-english name), using this expression for each datadaset:

```{r}
	granada.data$orderScaled<-seq_along(granada.data$contributions)/length(granada.data$contributions)
	malaga.data$orderScaled<-seq_along(malaga.data$contributions)/length(malaga.data$contributions)
	sevilla.data$orderScaled<-seq_along(sevilla.data$contributions)/length(sevilla.data$contributions)
	valencia.data$orderScaled<-seq_along(valencia.data$contributions)/length(valencia.data$contributions)
	barcelona.data$orderScaled<-seq_along(barcelona.data$contributions)/length(barcelona.data$contributions)
	madrid.data$orderScaled<-seq_along(madrid.data$contributions)/length(madrid.data$contributions)
	almeria.data$orderScaled<-seq_along(almeria.data$contributions)/length(almeria.data$contributions)
	zaragoza.data$orderScaled<-seq_along(zaragoza.data$contributions)/length(zaragoza.data$contributions)
	jaen.data$orderScaled<-seq_along(jaen.data$contributions)/length(jaen.data$contributions)
	cadiz.data$orderScaled<-seq_along(cadiz.data$contributions)/length(cadiz.data$contributions)
	bilbao.data$orderScaled<-seq_along(bilbao.data$contributions)/length(bilbao.data$contributions)	
	huelva.data$orderScaled<-seq_along(huelva.data$contributions)/length(huelva.data$contributions)
	cordoba.data$orderScaled<-seq_along(cordoba.data$contributions)/length(cordoba.data$contributions)
	spain.data$orderScaled<-seq_along(spain.data$contributions)/length(spain.data$contributions)

```

We plot the new data seem a not bad fit of most of the data:

```{r}

	library("ggplot2")
	ggplot() + geom_point(data=zaragoza.data,aes(x=orderScaled,y=log10(contributions),color='ZGZ')) + 
	geom_point(aes(y=log10(almeria.data$contributions),x=almeria.data$orderScaled,color='almeria.data$contributions')) + 
	geom_point(aes(y=log10(madrid.data$contributions),x=madrid.data$orderScaled,color='madrid.data$contributions')) + 
	geom_point(aes(y=log10(barcelona.data$contributions),x=barcelona.data$orderScaled,color='barcelona.data$contributions')) + 
	geom_point(aes(y=log10(spain.data$contributions),x=spain.data$orderScaled,color='spain.data$contributions')) +
	geom_point(aes(y=log10(malaga.data$contributions),x=malaga.data$orderScaled,color='malaga.data$contributions')) +
	geom_point(aes(y=log10(sevilla.data$contributions),x=sevilla.data$orderScaled,color='sevilla.data$contributions')) +
	geom_point(aes(y=log10(granada.data$contributions),x=granada.data$orderScaled,color='granada.data$contributions')) +
	geom_point(aes(y=log10(bilbao.data$contributions),x=bilbao.data$orderScaled,color='bilbao.data$contributions')) +
	geom_point(aes(y=log10(cordoba.data$contributions),x=cordoba.data$orderScaled,color='cordoba.data$contributions')) +
	geom_point(aes(y=log10(jaen.data$contributions),x=jaen.data$orderScaled,color='jaen.data$contributions'))
	
```

Looking in more detail to the chart we can notice that Granada show a extrange efect that we call  the "JJ efect" where there is a lot of user with low number of contribution

## JJ efect is clearly visible in Granada

### Plot with Granada

```{r plot_with_granada}
qplot(zaragoza.data$orderScaled,log10(zaragoza.data$contributions)) + 
geom_point(aes(y=log10(almeria.data$contributions),x=almeria.data$orderScaled,color='almeria.data$contributions')) + 
geom_point(aes(y=log10(madrid.data$contributions),x=madrid.data$orderScaled,color='madrid.data$contributions')) + 
geom_point(aes(y=log10(barcelona.data$contributions),x=barcelona.data$orderScaled,color='barcelona.data$contributions')) + 
geom_point(aes(y=log10(spain.data$contributions),x=spain.data$orderScaled,color='spain.data$contributions')) +
geom_point(aes(y=log10(malaga.data$contributions),x=malaga.data$orderScaled,color='malaga.data$contributions')) +
geom_point(aes(y=log10(sevilla.data$contributions),x=sevilla.data$orderScaled,color='sevilla.data$contributions')) +
geom_point(aes(y=log10(granada.data$contributions),x=granada.data$orderScaled,color='granada.data$contributions')) +
geom_point(aes(y=log10(bilbao.data$contributions),x=bilbao.data$orderScaled,color='bilbao.data$contributions')) +
geom_point(aes(y=log10(cordoba.data$contributions),x=cordoba.data$orderScaled,color='cordoba.data$contributions')) +
geom_point(aes(y=log10(jaen.data$contributions),x=jaen.data$orderScaled,color='jaen.data$contributions'))
```

### Plot without Granada

```{r plot_wo_grx}
qplot(zaragoza.data$orderScaled,log10(zaragoza.data$contributions)) + 
geom_point(aes(y=log10(almeria.data$contributions),x=almeria.data$orderScaled,color='almeria.data$contributions')) + 
geom_point(aes(y=log10(madrid.data$contributions),x=madrid.data$orderScaled,color='madrid.data$contributions')) + 
geom_point(aes(y=log10(barcelona.data$contributions),x=barcelona.data$orderScaled,color='barcelona.data$contributions')) + 
geom_point(aes(y=log10(spain.data$contributions),x=spain.data$orderScaled,color='spain.data$contributions')) +
geom_point(aes(y=log10(malaga.data$contributions),x=malaga.data$orderScaled,color='malaga.data$contributions')) +
geom_point(aes(y=log10(sevilla.data$contributions),x=sevilla.data$orderScaled,color='sevilla.data$contributions')) +
geom_point(aes(y=log10(bilbao.data$contributions),x=bilbao.data$orderScaled,color='bilbao.data$contributions')) +
geom_point(aes(y=log10(cordoba.data$contributions),x=cordoba.data$orderScaled,color='cordoba.data$contributions')) +
geom_point(aes(y=log10(jaen.data$contributions),x=jaen.data$orderScaled,color='jaen.data$contributions'))
```

The spain chart shows a different efect that we will investigate in a near future ;)
